### 2022-05-17 README.Rmd
update renv instructions and roadmap

This repository contains data and code for a manuscript by Eric Scott and Emilio Bruna written for submission to The American Naturalist tentatively titled: \_\_\_\_\_.

@@

-   [x] Finish building all IPMs
-   [x] Document functions and \_targets.R
-   [ ] Calculate bootstrapped 95% CIs around all lambdas
-   [ ] Finish writing methods section
-   [ ] Draft tables & figures
-   [ ] Archive draft of code in Zenodo

@@

-   Open the project in RStudio by double-clicking the `.Rproj` file.
-   Install packages listed in `packages.R` (if this compendium uses `renv`, this may happen automatically or with `renv::restore()`).
-   Install the [`targets` package](https://docs.ropensci.org/targets/).
-   Run `targets::tar_make()` or `targets::tar_make_clustermq()` from the R console to run all code and produce all outputs.

>>>>

This repository contains data and code for a manuscript by Eric Scott and Emilio Bruna written for submission to The American Naturalist tentatively titled: *Context-dependent consequences of including lagged effects in demographic models*.

@@

-   [x] Finish building all IPMs
-   [x] Document functions and \_targets.R
-   [ ] Calculate bootstrapped 95% CIs around all lambdas
-   [x] Finish draft of methods section
-   [x] Draft tables & figures
-   [ ] Archive draft of code in Zenodo

@@

-   Open the project in RStudio by double-clicking the `.Rproj` file.
-   This project uses `renv` for package management, which should be installed automatically when opening the project. Run `renv::restore()` to install all required packages.
-   Run `targets::tar_make()` or `targets::tar_make_clustermq()` from the R console to run all code and produce all outputs.
